---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# epicsawrap: R Package for Integrating rpicsa and epicsadata Functions for API Apps

<!-- badges: start -->
[![R-CMD-check](https://github.com/IDEMSInternational/epicsawrap/workflows/R-CMD-check/badge.svg)](https://github.com/IDEMSInternational/epicsawrap/actions)
[![Codecov test
coverage](https://codecov.io/gh/IDEMSInternational/epicsawrap/branch/main/graph/badge.svg)](https://app.codecov.io/gh/IDEMSInternational/epicsawrap?branch=main)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Overview

**epicsawrap** is an R package that brings together the functionality of **rpicsa** and **epicsadata** packages to be used in creating API applications for crop and climate analysis. It provides a convenient interface for accessing and utilizing the functions from both packages, enabling the development of web-based tools and services for agricultural decision support.

The package combines the capabilities of **rpicsa** for PICSA and climatic analysis for crops with **epicsadata** for retrieving climate and weather data, creating a powerful tool for addressing the needs of farmers, agronomists, and researchers.

## Installation

You can install **epicsawrap** from CRAN using the following command:

``` r
# Install the 'devtools' package if you haven't already
if (!require(devtools)) {
  install.packages("devtools")
}

# Install 'epicsawrap' from GitHub
devtools::install_github("IDEMSInternational/epicsawrap")
```


## Documentation
For detailed information on each function, including arguments, usage, and examples, please refer to the package documentation. You can access it using the following command:

```{r, message = FALSE, warning = FALSE, eval=FALSE, include=TRUE}
?epicsawrap
```

The GitHub page for the `rpicsa` package can be found [here](https://github.com/IDEMSInternational/rpicsa).
The GitHub page for the `epicsadata` package can be found [here](https://github.com/IDEMSInternational/epicsadata).

## Contributing
We welcome contributions from the community. If you have any bug reports, feature requests, or would like to contribute code to rpicsa, please visit our GitHub repository.

## License
This package is open-source and distributed under the GNU Lesser General Public License v3.0 License. Feel free to use, modify, and distribute it as needed.

## Contact
If you have any questions, suggestions, or feedback, please feel free to reach out to us.